Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-14 ms.tex
f1 map figure caption
clarify that we use the Planck+DIRBE revised global parameters by default in full-resolution fits

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
fixed, while the dust spectrum normalization and dust temperatures are allowed 
to vary for each line-of-sight. In order to predict the dust SED for a given 
pixel, we are thus left with two remaining degrees of freedom, and must 
choose an appropriate set of two parameters to sample and thereby constrain via
MCMC. To determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the `IRAS convention' intensity in the 545 GHz bandpass, 
as defined in Equation \ref{eqn:inten}. With the four aforementioned global 
parameters fixed, the dust spectrum shape is determined entirely by the two 
dust temperatures, which are coupled. To constrain the dust temperatures,
 we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby determining the temperature
and emissivity power law index for both MBB components and thus fully 
specifying the SED shape. In principle, we could sample in either $T_1$ or 
$T_2$, but have chosen to sample in $T_2$ because emission from this component 
dominates in the relatively high frequency bands which most strongly constrain 
the dust temperatures.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} The results of our low-resolution fit with $f_1$
allowed to vary.}
\end{center}
\end{figure}

>>>>

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
fixed. By default, we employ the best-fit \PLANCK+DIRBE global parameters of 
Table \ref{tab:global}, model 2, although our data release 
($\S$\ref{sec:release}) includes fits with the FDS99 global parameters as well.
Still,  the dust spectrum normalization and dust temperatures are allowed to 
vary for each line-of-sight. In order to predict the dust SED for a given 
pixel, we are thus left with two remaining degrees of freedom, and must choose 
an appropriate set of two parameters to sample and thereby constrain via MCMC. 
To determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the `IRAS convention' intensity in the 545 GHz bandpass, as 
defined in Equation \ref{eqn:inten}. With the four aforementioned global 
parameters fixed, the dust spectrum shape is determined entirely by the two 
dust temperatures, which are coupled. To constrain the dust temperatures, we 
sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we compute
the corresponding value of $T_1$, thereby determining the temperature and 
emissivity power law index for both MBB components and thus fully specifying 
the SED shape. In principle, we could sample in either $T_1$ or $T_2$, but have
chosen to sample in $T_2$ because emission from this component dominates in the
relatively high frequency bands which most strongly constrain the dust 
temperatures.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} The $1^{\circ}$ FWHM map of $f_1$ derived from our 
low-resolution fit in which $f_1$ is allowed to vary spatially.}
\end{center}
\end{figure}
